---
title: "Board Games Database"
author: "Tamara Nold"
TidyTuesday: "https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-03-12"
output: html_document
---

# Load packages
```{r}
library(tidyverse)
library(ggplot2)
library(summarytools)
```

# Import data
```{r}
board_games <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-12/board_games.csv")

view(dfSummary(board_games))

```

# Thoughts 
As a board gamer, I want to know which game I missed and how to find the best games. 

Filter for interesting variables:
```{r}
games_sub <- board_games %>%
  select(name,
         users_rated, 
         average_rating, 
         playing_time,
         min_age, 
         min_players, 
         max_players,
         category,
         mechanic, 
         designer, 
         expansion, 
         publisher)

view(dfSummary(games_sub))
```


# Which game is a must-have?
```{r}
games_sub %>%
  top_n(20, average_rating) %>%
  ggplot(aes(x = fct_reorder(name, average_rating), 
             y = average_rating, 
             size = users_rated, 
             color = users_rated)) + 
  geom_point() + 
  labs(title = "Which Game is a Must-Have?",
       subtitle = "Top 20 Board Games by Score", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light() +
  theme(legend.position = "none")
```

# Which game is a must-have by category?
```{r}
top_category <- games_sub %>%
  separate_rows(category, sep = ",") %>%
  count(category) %>%
  top_n(20, n) %>%
  select(category) %>%
  unlist()

games_sub %>%
  filter(category %in% top_category) %>%
  ggplot(aes(x = category, 
             y = average_rating)) + 
  geom_boxplot() + 
  labs(title = "Top 20 Board Games Categories by Score",
       x = "", 
       y = "Average rating (1-10)") +
  coord_flip() +
  theme_light() +
  theme(legend.position = "none")

games_sub %>%
  filter(category %in% top_category) %>%
  group_by(category) %>%
  top_n(1, average_rating) %>%
  select(category, name, average_rating, users_rated) %>%
  ggplot(aes(x = fct_reorder(category, average_rating), 
             y = average_rating, 
             size = users_rated, 
             color = users_rated)) +
  geom_point() +
  geom_text(aes(label = name), check_overlap = T, show.legend = F, size = 3, color = "black") +
  labs(title = "Which Game is a must-have by Category?",
       subtitle = "Top 20 of most extensive Sategories", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light() +
  theme(legend.position = "none")


```
# Which publisher has a guarantee of success?
```{r}
top_publisher <- games_sub %>%
  separate_rows(publisher, sep = ",") %>%
  group_by(publisher) %>%
  summarise(max_rating = max(average_rating)) %>%
  top_n(20, max_rating) %>%
  select(publisher) %>% 
  ungroup() %>%
  unlist()
  
games_sub %>%
  separate_rows(publisher, sep = ",") %>%
  filter(publisher %in% top_publisher) %>%
  ggplot(aes(x = fct_reorder(publisher, average_rating), 
             y = average_rating)) +
  geom_boxplot() +
  labs(title = "Which Publisher has a Guarantee of Success?",
       subtitle = "Games of the Top 20 Publishers by Score", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light() 

```

# Which publisher should stay at the store?
```{r}
flop_publisher <- games_sub %>%
  separate_rows(publisher, sep = ",") %>%
  group_by(publisher) %>%
  summarise(min_rating = min(average_rating)) %>%
  top_n(20, desc(min_rating)) %>%
  select(publisher) %>% 
  ungroup() %>%
  unlist()
  
games_sub %>%
  separate_rows(publisher, sep = ",") %>%
  filter(publisher %in% flop_publisher) %>%
  ggplot(aes(x = fct_reorder(publisher, average_rating), 
             y = average_rating)) +
  geom_boxplot() +
  labs(title = "The Games of which Publisher should stay at the Store?",
       subtitle = "Games of the Flop 20 Publishers by Score", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light() 

```
# Which designer has a guarantee of success?
```{r}
top_designer <- games_sub %>%
  separate_rows(designer, sep = ",") %>%
  group_by(designer) %>%
  summarise(max_rating = max(average_rating)) %>%
  top_n(20, max_rating) %>%
  select(designer) %>% 
  ungroup() %>%
  unlist()

games_sub %>%
  separate_rows(designer, sep = ",") %>%
  filter(designer %in% top_designer) %>%
  ggplot(aes(x = fct_reorder(designer, average_rating), 
             y = average_rating)) +
  geom_boxplot() +
  labs(title = "Which Designer has a Guarantee of Success?",
       subtitle = "Top 20 Designers for Board Games by Score", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light() 
```


# Which designer has to learn more about games?
```{r}
flop_designer <- games_sub %>%
  separate_rows(designer, sep = ",") %>%
  group_by(designer) %>%
  summarise(min_rating = min(average_rating)) %>%
  top_n(20, desc(min_rating)) %>%
  select(designer) %>% 
  ungroup() %>%
  unlist()

games_sub %>%
  separate_rows(designer, sep = ",") %>%
  filter(designer %in% flop_designer) %>%
  ggplot(aes(x = fct_reorder(designer, average_rating), 
             y = average_rating)) +
  geom_boxplot() +
  labs(title = "Which Designer has to learn more about Games?",
       subtitle = "Flop 20 Designers for Board Games by Score", 
       x = "", 
       y = "Average rating (1-10)",
       caption = "(based on data from Board Games Geek)") +
  coord_flip() +
  theme_light()
```



# Can I find a great game just from a look at the packeging?
```{r}
games_lm <- games_sub %>%
  mutate(expansion = ifelse(is.na(expansion), 0, 1),
         top_pub = ifelse(publisher %in% top_publisher, 1, 0))

lm <- lm(average_rating ~ playing_time +
         min_age + 
         min_players +
         max_players +
         expansion,
         data = games_lm)

summary(lm)
```

